PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-13 paper/paper.tex
Add small fixes
- hyphenation of 'Dittmaier'
- don't use small caps PineAPPL in titles, latex doesn't do that
- use pt of the sum of the two leptons instead of the Z boson
- use SIrange for percentage ranges
Specify W-boson parameters and Gmu
These parameters enter in the definition of the EW coupling and
explicitly in some virtuals

\usepackage[UKenglish]{babel}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage[binary-units=true,detect-weight=true,table-format=4.2]{siunitx}
\usepackage{xcolor}
\usepackage[percent]{overpic}
\usepackage{mathcomp}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{xltabular}

@@

\acknowledgments
We are grateful to Rikkert Frederix for discussions about
\textsc{aMCfast}, and to Stefan Dittmaier for a critical reading of the
manuscript. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data.
%Alessandro Vicini\\
S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
E.R.N.\ is supported by the European Commission through a Marie
Sk\l odowska-Curie Action (grant agreement no.\ 752748).
M.Z.\ thanks the Nikhef institute in Amsterdam,
where he was employed when this paper was started.

>>>>

\usepackage[UKenglish]{babel}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage[binary-units=true,detect-weight=true,digitsep=none,table-format=4.2]{siunitx}
\usepackage{xcolor}
\usepackage[percent]{overpic}
\usepackage{mathcomp}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{xltabular}

@@

\acknowledgments
We are grateful to Rikkert Frederix for discussions about
\textsc{aMCfast}, and to Stefan Ditt\-mai\-er for a critical reading of the
manuscript. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data.
%Alessandro Vicini\\
S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
E.R.N.\ is supported by the European Commission through a Marie
Sk\l odowska-Curie Action (grant agreement no.\ 752748).
M.Z.\ thanks the Nikhef institute in Amsterdam,
where he was employed when this paper was started.

### 2020-08-13 paper/sec-results.tex
Specify W-boson parameters and Gmu
These parameters enter in the definition of the EW coupling and
explicitly in some virtuals

The values of the relevant physical parameters are chosen as
\begin{equation}
%\begin{aligned}
%M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
M_\mathrm{Z} = \SI{91.176}{\giga\electronvolt} \text{,} \quad 
m_\mathrm{t} = \SI{172.5}{\giga\electronvolt} \text{,} \quad 
%\Gamma_\mathrm{W} &= \SI{2.09}{\giga\electronvolt} \text{,} &
\Gamma_\mathrm{Z} = \SI{2.50}{\giga\electronvolt} \text{,}
%\end{aligned}
\label{eq:parameters}
\end{equation}
where $M_\mathrm{Z}$ and $m_\mathrm{t}$ are the values of the Z-boson, and
top-quark masses, respectively, and $\Gamma_\mathrm{Z}$ is the width of
the Z boson. The value of the strong
coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.

>>>>

The values of the relevant physical parameters are chosen as
\begin{equation}
\begin{aligned}
M_\mathrm{W} &= \SI{80.419}{\giga\electronvolt} \text{,} \quad &
M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
\Gamma_\mathrm{W} &= \SI{2.09291}{\giga\electronvolt} \text{,} &
\Gamma_\mathrm{Z} &= \SI{2.49877}{\giga\electronvolt} \text{,} &
G_\mu &= \SI{1.16639e-5}{\per\giga\electronvolt\squared} \text{,}
\end{aligned}
\label{eq:parameters}
\end{equation}
where $M_\mathrm{Z}$, $M_\mathrm{W}$, $m_\mathrm{t}$ are the values of the Z-boson, W-boson, and
top-quark masses, respectively, $\Gamma_\mathrm{Z}$ and $\Gamma_\mathrm{W}$ are the widths of
the Z and W bosons, and $G_\mu$ is value of the Fermi coupling. The value of the strong
coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.
